Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-20 notes.tex
completed self energy part, and incorporated sir's edits as well

The index $n$ actually defines a set of quantum numbers that characterize the state $\ket{n}$. For example it might be a combination of number of particles, parity and total spin angular momentum $(n \equiv n, P, S^z)$. One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other. The set of eigenstates that have the total number of particles equal to $N+1$ will then form the basis in question. Since the dimer is decoupled from the bath, the total wavefunction will be a direct product of a Hubbard dimer wavefunction and a bath wavefunction.

@@

$\alpha$ is an internal quantum number of the Hubbard dimer while $\beta$ is that for the bath. The subscripts $m$ and $N-m+1$ label the total number of particles in each part of the wavefunction. These two labels have to add to $N+1$. Using this expansion, the matrix element of $\mathcal{G}$ can be written as

@@

The matrix elements for hole propagation are obtained similarly. Here the relavant excitations are $\ket{\overline{i\sigma}} \equiv c_{i\sigma}\ket{0}$, at frequency $-\omega$. To expand these states, we choose the $N-1$ eigenstates as the orthonormal basis:

@@

\subsection{Constructing full Greens function matrix from the inverse matrix via Fourier transformation to \(k-\)space}

@@

The spectral weights remain unchanged; only the matrix element changes from $A_nm$ to $(A^{-1})_{nm}$. Inverting the matrix $\mathcal{G}_D$ is actually simple because it is diagonal in the chosen basis:

@@

	\left(\mathcal{G}^{-1}_D\right)_{nn} = \begin{pmatrix} g_{0} & 0 & & \\ 0 & g_{1} & & \\ && .. &  \\ &&& g_{M} \end{pmatrix} \implies \left(\mathcal{G}_D\right)_{nn} = \begin{pmatrix} \frac{1}{g_0} & 0 & \\ 0 & \frac{1}{g_1} & \\ && ... & \\ &&& \frac{1}{g_M}\end{pmatrix}

@@

\subsection{Calculation of self energy matrix from the Dyson equation}
Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
\Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
&=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k}
This is the full self energy matrix. One can get both real space and momentum space self energies by taking appropriate matrix elements. For instance, the self-energy in momentum space is
	\label{selfenergy}
	\Sigma_{H} (\vec{k},\omega) \equiv \bra{\vec k} \Sigma_H (\omega) \ket{\vec k} = \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.

>>>>

where $C^{0}$ and $C^{1}$ are coefficients of the linear superposition defined by
C^{0}_{n} = \bra{n} c^\dagger_{0\sigma}\ket{0}~,~ C^{1}_{n} = \bra{n} c^\dagger_{1\sigma}\ket{0}~.
Due to the translation invariance, the coefficients $C^{0}_{n}$ and $C^{1}_{n}$ are independent of the site indices. The index $n$ actually defines a set of quantum numbers that characterize the state $\ket{n}$. For example it might be a combination of number of particles, parity and total spin angular momentum $(n \equiv n, P, S^z)$. One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other. The set of eigenstates that have the total number of particles equal to $N+1$ will then form the basis in question. Since the dimer is decoupled from the bath, the total wavefunction will be a direct product of a Hubbard dimer wavefunction and a bath wavefunction.

@@

$\alpha$ is an internal quantum number of the Hubbard dimer while $\beta$ is that for the bath. The subscripts $m$ and $N-m+1$ label the total number of particles in each part of the wavefunction. These two labels have to add to $N+1$. Our choice of the $\ket{n}$ is motivated by noting that the effective auxiliary model we are invoking here is that of a Hubbard dimer connected to a bath via single-particle hybridisation; the eigenstates of the isolated dimer and bath subsystems then act as the natural choices of the orthogonal bases in which to expand the wavefunction for the single-particle excitation of the interacting system $c^\dagger_{0\sigma}\ket{0}$. Further, while the eigenstates ($\Phi^D_{m,\alpha}$) of the Hubbard dimer are known analytically, we can safely assume the eigenstates of the bath ($\Psi^B_{N-m+1, \beta}$) to be a simple direct product of various single-particle Fock states in $k$-space. We then compute the matrix element of eq.\eqref{local_gf} for site $i$ and its immediate neighbours (i.e., a given realisation of a auxiliary model). Then, using translation invariance, we demand that this matrix element is independent of the site index $i$. The correctness of this auxiliary model approach hinges on how close the state $\ket{\tilde{0}}$ is to the 2-site local nature of the exact ground state of the target model (here the Hubbard model on a given lattice). Further improvement can be made by improving (i) the state $\ket{\tilde{0}}$ for the present auxiliary model (involving a Hubbard dimer), or (ii) choosing a better auxiliary model with an ``impurity" system that has more sites than two (i.e., a Bethe-Peierls improvement of the dimer auxiliary model).
Using this expansion, the matrix element of $\mathcal{G}$ can be written as

@@

The matrix elements for hole propagation are obtained similarly. Here the relavant excitations are $\ket{\overline{i\sigma}} \equiv c_{i\sigma}\ket{0}$, at frequency $-\omega$. To expand these states, we choose the eigenstates with $N-1$ total particles as the orthonormal basis:

@@

\subsection{Constructing full Greens function matrix from the inverse matrix}

@@

The spectral weights remain unchanged; only the matrix element changes from $A_{nm}$ to $(A^{-1})_{nm}$. Inverting the matrix $\mathcal{G}_D$ is actually simple because it is diagonal in the chosen basis:

@@

	\left(\mathcal{G}^{-1}_D\right)_{nn} = \begin{pmatrix} g_{0} && 0 && &..& 0\\ 0 && g_{1} && && \\ &&..&& .. &&  \\ 0 &&&&&& g_{M} \end{pmatrix} \implies \left(\mathcal{G}_D\right)_{nn} = \begin{pmatrix} \frac{1}{g_0} & 0 & \\ 0 & \frac{1}{g_1} & \\ && ... & \\ &&& \frac{1}{g_M}\end{pmatrix}

@@

\subsection{Calculation of self energy matrix from the Dyson equation}
% Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
% \begin{eqnarray}
% \Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
% &=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k}
% \end{eqnarray}
% This is the full self energy matrix. One can get both real space and momentum space self energies by taking appropriate matrix elements. For instance, the self-energy in momentum space is
% \begin{equation}\begin{aligned}
% 	\label{selfenergy}
% 	\Sigma_{H} (\vec{k},\omega) \equiv \bra{\vec k} \Sigma_H (\omega) \ket{\vec k} = \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
% \end{aligned}\end{equation}
With the knowledge of the momentum-space Greens function $G_H(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
\begin{equation}\begin{aligned}
	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
\end{aligned}\end{equation}
where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system. Substituting this as well as the full Greens function $G_H(\vec k, \omega)$ into Dyson's equation gives
\begin{equation}\begin{aligned}
	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
\end{aligned}\end{equation}
